Luminance constancy under fixed geometry

### 2018-05-18 Draft5/draft5.tex
restructured

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
	\centering
	\caption{}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_a.png}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.55 \textwidth}   
        \caption{}    
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination. Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position. The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy. (b) Images of a sphere under a fixed illuminant.  Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.  The relative reflectance function (i.e. the shape of the spectral reflectance function) varies across each row.
Within each row, the light reflectance value (LRV) of the spheres is constant. The values on the left of each row provide the corresponding LRV. We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
 \end{figure}

Recently, supervised statistical learning methods have been applied to the computational problem of color constancy.
These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
This general statistical learning approach has been useful for other perceptual problems in early and mid-level vison. domains of vision. 
For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}. It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}. %% JDB: Please add 2012 reference that I will provide.
In this paper, we apply AMA to a special case of computational color constancy.

@@

% Figure 2
\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \caption{Library }
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_a.png}
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Mill}    
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_b.png}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Table-Chairs}    
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_c.png}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}
    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
\end{figure}
%% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. The panels show different objects inserted in the library base scene. The objects were inserted at a user defined location in the image. Then the rendering viewpoint was set so that the object is at the center of the rendered image. In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
\end{figure}
%% DHB: Can we render these examples at higher resolution, so that they look nicer?  The blurriness is distracting in the images.

% Figure 4
\begin{figure}
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target position}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_d.png}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target size/Orientation}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_e.png}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
~
\centering
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_a.png}
        \label{fig:targetVariation}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Illumination spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_c.png}
        \label{fig:illuminationVariation}
    \end{subfigure}
          ~  
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Background spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_b.png}
        \label{fig:backGroundVariation}
    \end{subfigure}

@@

% Figure 5: Conditions Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\caption{Condition 1}
%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
 		\label{fig:backgroundVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \caption{Condition 2}	
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.pdf}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
	\caption{Condition 3}	
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.pdf}        
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3. The numbers on the left indicate the standard luminance level of the target object. 5 images are shown at each luminance level. We studied three types of spectral variations. (a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable. The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.  Across the three panels, spheres in corresponding locations have the same surface reflectance. In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure. The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.} 
\label{fig:studiedCases}
\end{figure}
%% DHB: May also want to render these examples at a higher resolution

@@

For the primary results, we used the ``{\it Library}'' base scene and a spherical target object.
The library base scene contains 2 area lights. 
We inserted one additional spherical spherical light source into the scene.
The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
scenes in the database. The geometry is shown in Figure~\ref{fig:3DScene}.
Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra, as described below.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
\subsubsection{Illumination spectra}
% Figure 6
\begin{figure}
\centering
    \begin{subfigure}[b]{0.24 \textwidth}
    \centering
	\caption{Granada dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_a.pdf}
        \label{fig:granadaData}
    \end{subfigure}
	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_b.pdf}
        \label{fig:illuminantSamples}
    \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_c.pdf}
        \label{fig:xyDiagram}
        \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_d.pdf}
        \label{fig:sRGBIlluminant}
    \end{subfigure}
    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset. Each spectrum is normalized by its mean (with mean taken over wavelength). (b) Sample spectra generated using the statistical model derived from normalized Granada dataset. (c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red). F(d) sRGB renditions of the samples shown in b.}
\label{fig:illuminant}
\end{figure}

To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and then sampled randomly from the model (see appendix).
To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
to 31 evenly-spaced wavelengths between 400 nm and 700 nm.

@@

Our statistical model approximates the normalized Granada spectra using the first 6 principle components.
The variation in the weights on these components is modeled with a 6-dimensional Gaussian.
The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
% on these components obtained from the normalized Granada spectra 
To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
Details of the statistical model for illumination are provided in the appendix.
Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.

@@

\subsubsection{Surface reflectance spectra}
% Figure 7 Surface Reflectance Data and Model
\begin{figure}
\centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
            \caption{Munsell and Vrhel dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_a.pdf}
        \label{fig:reflectanceSpectra}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_b.pdf}
        \label{fig:reflectanceSamples}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
    \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_c.pdf}
        \label{fig:xyChroReflectance}
    \end{subfigure}    
    \centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_d.pdf}
        \label{fig:backgroundSwatches}
    \end{subfigure}
    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets. (b) Sample spectra generated using the surface reflectance statistical model. (c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances and samples shown in b (red). (d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
\label{fig:surfaceReflectanceGeneration}
\end{figure}

%Figure 8 Target Surface Reflectance Samples
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure8/Figure8.pdf}
\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum. The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6]. Each row contains 10 random samples of reflectance spectra generated at the LRV shown on the left.}
\label{fig:targetSwatches}
\end{figure}

@@

For generating the target object reflectance at a particular luminance, the generated reflectance spectrum was 
scaled such that the LRV had the desired value (see appendix).
Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
%% DHB: Note that this procedure is different than conditioning the statistical model on the target LRV.  We could switch to the latter if we wished.
%% VS: I don't think it matters if we care about keeping only one color co-ordinate fixed.

% Figure 8: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \caption{sRGB rendering of a 3D scene}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_a.png}
        \label{fig:3DScene}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \caption{Cropped image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_b.png}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \caption{Retinal image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_c.png}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \caption{LMS normalized cone contrast}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_d.png}
        \label{fig:coneContrast}
    \end{subfigure}
    \label{fig:sceneWithCroppedImage}
    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created. The rendering viewpoint is selected so that the target object is in the center of the image. Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text. A multispectral image of the scene is then rendered. (b) The central portion of the rendered image, which contains the target object, is cropped. (c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors. The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).  (d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing). Finally, the demosaiced images are contrast normalized separately for each cone type.}
\end{figure}

@@

In Condition 1, only the LRV and relative reflectance spectrum of the target object vary across scenes.
For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
preserved LRV (which is calculated using a CIE D65 as the illumination).
% JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods) and thus expect a reasonable degree of similarity to D65.
%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
% our graphics approach to understand, and we want to build up examples.
% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.

>>>>

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
	\centering
	\caption{}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.55 \textwidth}   
        \caption{}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination. Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position. The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy. (b) Images of a sphere under a fixed illuminant.  Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.  The relative reflectance function (i.e. the shape of the spectral reflectance function) varies across each row.
Within each row, the light reflectance value (LRV) of the spheres is constant. The values on the left of each row provide the corresponding LRV. We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
 \end{figure}

Recently, supervised statistical learning methods have been applied to the computational problem of color constancy.
These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
This general statistical learning approach has been useful for other perceptual problems in early and mid-level vison. domains of vision. 
For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}. It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
In this paper, we apply AMA to a special case of computational color constancy.

@@

% Figure 2
\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \caption{Library }
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Mill}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.png}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Table-Chairs}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.png}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}
    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
\end{figure}
%% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. The panels show different objects inserted in the library base scene. The objects were inserted at a user defined location in the image. Then the rendering viewpoint was set so that the object is at the center of the rendered image. In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
\end{figure}
%% DHB: Can we render these examples at higher resolution, so that they look nicer?  The blurriness is distracting in the images.

% Figure 4
\begin{figure}
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target position}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.png}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target size/Orientation}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.png}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
~
\centering
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Target spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.png}
        \label{fig:targetVariation}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Illumination spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.png}
        \label{fig:illuminationVariation}
    \end{subfigure}
          ~  
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \caption{Background spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.png}
        \label{fig:backGroundVariation}
    \end{subfigure}

@@

% Figure 5: Conditions Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\caption{Condition 1}
%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
 		\label{fig:backgroundVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \caption{Condition 2}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
	\caption{Condition 3}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3. The numbers on the left indicate the standard luminance level of the target object. 5 images are shown at each luminance level. We studied three types of spectral variations. (a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable. The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.  Across the three panels, spheres in corresponding locations have the same surface reflectance. In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure. The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.} 
\label{fig:studiedCases}
\end{figure}

@@

For the primary results, we used the ``{\it Library}'' base scene and a spherical target object.
The library base scene contains 2 area lights. 
We inserted one additional spherical spherical light source into the scene.
The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
scenes in the database. The geometry is shown in Figure~\ref{fig:3DScene}.
Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra, as described below.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
\subsubsection{Illumination spectra}
% Figure 6
\begin{figure}
\centering
    \begin{subfigure}[b]{0.24 \textwidth}
    \centering
	\caption{Granada dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
        \label{fig:granadaData}
    \end{subfigure}
	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
        \label{fig:illuminantSamples}
    \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
        \label{fig:xyDiagram}
        \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
        \label{fig:sRGBIlluminant}
    \end{subfigure}
    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset. Each spectrum is normalized by its mean (with mean taken over wavelength). (b) Sample spectra generated using the statistical model derived from normalized Granada dataset. (c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red). (d) sRGB renditions of the samples shown in b.}
\label{fig:illuminant}
\end{figure}

To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model (see appendix).
To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
to 31 evenly-spaced wavelengths between 400 nm and 700 nm.

@@

Our statistical model approximates the normalized Granada spectra using the first 6 principle components.
The variation in the weights on these components is modeled with a 6-dimensional Gaussian.
The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
Details of the statistical model for illumination are provided in the appendix.
Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.

@@

\subsubsection{Surface reflectance spectra}
% Figure 7 Surface Reflectance Data and Model
\begin{figure}
\centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
            \caption{Munsell and Vrhel dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
        \label{fig:reflectanceSpectra}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
        \label{fig:reflectanceSamples}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
    \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
        \label{fig:xyChroReflectance}
    \end{subfigure}    
    \centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
        \label{fig:backgroundSwatches}
    \end{subfigure}
    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets. (b) Sample spectra generated using the surface reflectance statistical model. (c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances and samples shown in b (red). (d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
\label{fig:surfaceReflectanceGeneration}
\end{figure}

%Figure 8 Target Surface Reflectance Samples
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure8/Figure8.pdf}
\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum. The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6]. Each row contains 10 random samples of reflectance spectra generated at the LRV shown on the left.}
\label{fig:targetSwatches}
\end{figure}

@@

For generating the target object reflectance at a particular luminance, the generated reflectance spectrum was 
scaled such that the LRV had the desired value (see appendix).
Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.

% Figure 8: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \caption{sRGB rendering of a 3D scene}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
        \label{fig:3DScene}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \caption{Cropped image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \caption{Retinal image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \caption{Normalized cone contrast}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
        \label{fig:coneContrast}
    \end{subfigure}
    \label{fig:sceneWithCroppedImage}
    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created. The rendering viewpoint is selected so that the target object is in the center of the image. Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text. A multispectral image of the scene is then rendered. (b) The central portion of the rendered image, which contains the target object, is cropped. (c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors. The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).  (d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing). Finally, the demosaiced images are contrast normalized.}
\end{figure}

@@

In Condition 1, only the LRV and relative reflectance spectrum of the target object vary across scenes.
For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
preserved LRV (which is calculated using a CIE D65 as the illumination).
% JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
% VS: We should say, the only source of variation that we have introduced preserved LRV
Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods) and thus expect a reasonable degree of similarity to D65.
%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
% our graphics approach to understand, and we want to build up examples.
% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.
